Model validation plots

### 2021-08-13 doc/validate_models.Rmd
add gam.check with no plot #92
track html outputs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## target knits Rmds in their own session, so load libraries here.
library(targets)
library(statmod)
library(tidyverse)
library(gratia)
library(mgcv)
library(dlnm)
library(arm)
```

@@

```{r, echo=FALSE}
withr::with_dir(here::here(),{
  tar_load(c(s_1ha, s_cf, s_cf_sub))
})
```

@@

```{r echo=TRUE}
s_1ha_res <- qresid(s_1ha)
par(mfrow = c(2,2))
#histogram
plot(density(s_1ha_res))
#QQ plot
qqnorm(s_1ha_res); qqline(s_1ha_res)
#Fitted vs. residuals--binned residuals plot
binnedplot(fitted(s_1ha), residuals(s_1ha, type = "response"))
```

@@

```{r}
# gam.check(s_1ha)
```

@@

```{r}
# looking for near zero edf
gam(s_1ha_res ~ s(log_size_prev, k = 10, bs = "cs"), gamma = 1.4,
    data = model.frame(s_1ha)) #fine

@@

```{r}
summary(s_1ha)
```

```{r}
draw(s_1ha)
```

@@

@@

@@

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
## target knits Rmds in their own session, so load libraries here.
library(targets)
library(statmod)
library(tidyverse)
library(gratia)
library(mgcv)
library(dlnm)
library(arm)
```

@@

```{r, echo=FALSE, eval=TRUE}
withr::with_dir(here::here(),{
  tar_load(c(s_1ha, s_cf, s_cf_sub))
})
```

@@

```{r echo=TRUE, eval=TRUE}
s_1ha_res <- qresid(s_1ha)
par(mfrow = c(2,2))
#histogram
plot(density(s_1ha_res))
#QQ plot
qqnorm(s_1ha_res); qqline(s_1ha_res)
#Fitted vs. residuals--binned residuals plot
binnedplot(fitted(s_1ha), residuals(s_1ha, type = "response"))
```

@@

```{r eval=TRUE}
pdf(NULL)
gam.check(s_1ha)
dev.off()
```

@@

```{r eval=TRUE}
# looking for near zero edf
gam(s_1ha_res ~ s(log_size_prev, k = 10, bs = "cs"), gamma = 1.4,
    data = model.frame(s_1ha)) #fine

@@

```{r eval=TRUE}
summary(s_1ha)
```

```{r eval=TRUE}
draw(s_1ha)
```

@@

```{r}
pdf(NULL)
gam.check(s_cf)
dev.off()
```

@@

```{r}
pdf(NULL)
gam.check(g_1ha)
dev.off()
```

@@

```{r}
pdf(NULL)
gam.check(g_cf)
dev.off()
```

@@

```{r}
pdf(NULL)
gam.check(f_1ha)
dev.off()
```

@@

```{r}
pdf(NULL)
gam.check(f_cf)
dev.off()
```
